Entropy stable reduced order modeling of nonlinear conservation laws

### 2020-02-27 docs/ESDG_ROM/main.tex
deleting a bunch of stuff and staging old changes

Future work will aim to address computational costs associated with entropy stable reduced models.  Unlike standard hyper-reduction techniques, the number of nonlinear evaluations necessary scales with $O(N_s^2)$ rather than $O(N_s)$, where $N_s$ is the number of hyper-reduced sampling points.  This discrepancy is due to the fact that the hyper-reduction presented here approximates a nonlinear matrix, rather than a nonlinear vector.  These costs can be reduced by combining domain decomposition \cite{lucia2003reduced} and a discontinuous Galerkin-type discretization \cite{chan2017discretely} to produce multi-domain reduced order models.  Suppose there are $k = 1,\ldots, K$ subdomains.  Then, this sort of multi-domain model is expected to reduce costs if the sum of the squares of the number of subdomain sampling points $\sum_k (N_s^k)^2$ is significantly smaller than the global number of sampling points $N_s^2$.  Future work will also investigate implicit time-stepping for entropy stable reduced models, as additional costs associated with the spatial formulation may be offset by the reduction in cost for solving smaller matrix systems during the linearization process.

>>>>

Future work will aim to address computational costs associated with entropy stable reduced models.  Unlike standard hyper-reduction techniques, the number of nonlinear evaluations necessary scales with $O(N_s^2)$ rather than $O(N_s)$, where $N_s$ is the number of hyper-reduced sampling points.  This discrepancy is due to the fact that the hyper-reduction presented here approximates a nonlinear matrix, rather than a nonlinear vector.  These costs can be reduced by combining domain decomposition \cite{lucia2003reduced} and a discontinuous Galerkin-type discretization \cite{chan2017discretely} to produce multi-domain reduced order models.  Suppose there are $k = 1,\ldots, K$ subdomains.  Then, a multi-domain reduced order model is expected to decrease costs if the sum of the squares of the number of subdomain sampling points $\sum_k (N_s^k)^2$ is significantly smaller than the global number of sampling points $N_s^2$.  Future work will also investigate implicit time-stepping for entropy stable reduced models, as additional costs associated with the spatial formulation may be offset by the reduction in cost for solving smaller matrix systems during the linearization process.
